Evolutionary Learning of Policies for MCTS Simulations

### 2012-05-10 presentation/presentation.tex
Added figures and results.

\begin{frame}{Evolutionary Learning}
\begin{itemize}
	\item Idea: Evolve playout policy
	\item Individual policies compete in a tournament to reproduce
	\item Self-play yields a self-bootstrapping system
\end{itemize}
\end{frame}

@@

\begin{frame}{Results}
\begin{itemize}
	\item Strong and robust
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Evolutionary Learning (Hivemind)}
\begin{itemize}
	\item Idea: Evolve playout policy
	\item Individual policies compete in a tournament to reproduce
	\item Self-play yields a self-bootstrapping system
\end{itemize}
\end{frame}

\begin{frame}{Evolution}
\begin{enumerate}
	\item Generate $n$ individuals (population)
	\item Evaluate fitness\label{eval}
	\item Rank by fitness
	\item Select top $c$ children, $c < n$
	\item Recombine children into $n$ new individuals (next generation)
	\item Mutate population
	\item Repeat from \ref{eval}
\end{enumerate}
\end{frame}

@@

\begin{frame}{Encoding - Example}
\begin{figure}
  \begin{center}
  \includegraphics[width=3.25in]{graphics/local-pattern.pdf}
  \label{fig:encoding}
  \end{center}
\end{figure}
\begin{itemize}
	\item Weight moves local to last-played move
	\item If local area is filled, use default policy
\end{itemize}
\end{frame}

\begin{frame}{Encoding - Example}
\begin{figure}
  \begin{center}
  \includegraphics[width=3.25in]{graphics/weight-pattern-map.pdf}
  \label{fig:encoding}
  \end{center}
\end{figure}
\begin{itemize}
	\item Map from 32-bit integer to floating point weight
	\item Evolution (mutation/recombination) operates on individual's map entries
\end{itemize}
\end{frame}

\begin{frame}{Results (Self)}
\begin{figure}
	\begin{center}
		\begin{tabular}{c | c c c}
		& \multispan{3}{\hfil opponent \hfil} \\
		 player & default & uniform & uniform (tenuki) \\
		\hline
		uniform & 70.50\% & & \\
		uniform (tenuki) & 61.00\% & 50.00\% & \\
		learned & 90.00\% & 84.00\% & 86.00\% \\
		\end{tabular}
	\label{fig:results}
	\end{center}
\end{figure}
All-play-all tournament of the 4 Hivemind variants.

Each element is the percent win-rate of the row variant versus the column variant.
\end{frame}

\begin{frame}{Results (Self)}
\centerline{
\begin{tabular}{c | cc cc}
 & \multispan{2}{\hfil default \hfil} & \multispan{2}{\hfil uniform local\hfil} \\
 & 11x11 & 13x13 & 11x11 & 13x13 \\ \hline
 learned win \%	& 92.5 \% & 94 \%  & 88.5\% & 85\% 
 \end{tabular}
}
\end{frame}

\begin{frame}{Results (MoHex 7x7)}
\centerline{
\begin{tabular}{lccc}
& Learned policy & Uniform local & Default policy \\
win \% & 42\% & 26\% & 11.75\%
\end{tabular}
}
\end{frame}

\begin{frame}{Results (MoHex 11x11)}
\centerline{
		\begin{tabular}{c  | c c c}
		Hivemind & Win-rate & Relative CPU \\
		\hline
		Default & 0.5\% & 510\% \\
		Local & 0.0\% & 545\% \\
		Learned & 11\% & 620\% \\
		\end{tabular}
}
\end{frame}
